Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-20 paper/main.tex
add info about individuals to results

@@

% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects.
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
% report here in group space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be found
in the accompanying dataset.
% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02 (m): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04 (f): PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05 (m): PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06 (m): PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09 (m): PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20 (f): PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer \citep{sengupta2016extension} shows ROIs in 12 of 14
subjects and unilateral right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Individual ROIs were assessed by visually inspecting unthresholded $z$-maps, and
setting a subjectively best fitting $z$-threshold to isolate a ROI that matched
the PPA.
% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of
sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
yielded only one cluster in the right hemisphere.
% AV
For the AV stimulus, results show homologous clusters in five subjects, and
unilateral right clusters in seven subjects (of which one subjects yielded a
unilateral cluster in the dedicated localizer).
% difference to dedicated localizer
We find bilateral clusters in sub-20, whereas the dedicated localizer yielded
only one cluster in the right hemisphere.

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
    cluster-corrected). To facilitate comparisons across subjects, individual
    brains are aligned via non-linear transformation to a study-specific T2*
    group template that is co-registered to the MNI152 template with an affine
    transformation (12 degrees of freedom).
    The results of audio-description's primary $t$-contrast (blue) that
    compares geometry-related nouns to non geometry-related nouns spoken by
    the audio-description's narrator (\texttt{geo, groom > all non-geo})
    are overlaid over the movie's primary $t$-contrast (blue) that compares
    cuts to new setting with cuts to a familiar perspective
    (\texttt{vse\_new > vpe\_old}).
    Black: outline of the subject-specific PPA ROIs.
    Light gray: The audio-description's field-of-view (cf.
    \citep{hanke2014audiomovie}).}
\label{fig:subs-thresh-ppa} \end{figure*}

>>>>

\todo[inline]{change coordinates of figure to z=-11 as it is in the slices of
individuals}

@@

% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects.
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
% report here in group space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be found
in the accompanying dataset.
% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02 (m): PPA (l/r), AO (-/-), AV (l/-); RSC: AO (-/-), AV (-/-)
% sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04 (f): PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05 (m): PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06 (m): PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09 (m): PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20 (f): PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer \citep{sengupta2016extension} shows ROIs in 12 of 14
subjects and unilateral right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Individual ROIs were assessed by visually inspecting unthresholded $z$-maps, and
setting a subjectively best fitting $z$-threshold to isolate a ROI that matched
the PPA.
% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of
sub-09 that within or overlapping with the PPA ROI.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% AV
For the AV stimulus, results show homologous clusters in five subjects,
unilateral right clusters in sixn subjects (of which one subjects yielded a
unilateral cluster in the dedicated localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated localizer yielded
only one cluster in the right hemisphere.

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of audio-description's primary
        $t$-contrast (blue) that compares geometry-related nouns to non
        geometry-related nouns spoken by the audio-description's narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to new setting with cuts
        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects. Thus, the figure does not depict the
        left cluster of the AV stimulus in sub-09 and sub-18, and the right
        cluster of the AV stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}
